Automated Residual Plot Assessment with the R Package autovi and the Shiny App autovi.web

### 2025-05-07 autovi_paper.qmd
Improve the rest of the first section

However, as discussed in @li2024automated, the lineup protocol has significant limitations in large-scale applications due to dependence on human labor. Thus, a computer vision model was developed with an associated statistical testing procedure to automate the assessment of residual plots. This model takes a residual plot and a vector of auxiliary variables (such as the number of observations) as inputs and outputs the predicted visual signal strength (VSS). This strength estimates the distance between the residual distribution of the fitted regression model and the reference distribution assumed under correct model specification.

To make the statistical testing procedure and trained computer vision model widely accessible, we developed the R package `autovi`, and a web interface, `autovi.web` to make it easy for users to automatically read their residual plots with the trained computer vision model.

>>>>

As noted in @li2024automated, the lineup protocol has significant limitations in large-scale applications due to its reliance on human labor. To overcome this constraint, a computer vision model was developed alongside a corresponding statistical testing procedure to autmoate the assessment of residual plots. The model takes as input a residual plot and a set of auxiliary variables (such as the number of observations) and outputs a predicted visual signal strength (VSS). This VSS estimates the degree of deviation between the residual distribution of the fitted model and the reference distribution expected under correct model specification.

To make the statistical testing procedure and trained computer vision model widely accessible, we developed the R package `autovi` along with a companion web interface, `autovi.web`, which allows users to automatically assess their residual plots using the trained computer vision model.

### 2025-05-07 autovi_paper.tex
Improve the rest of the first section

However, as discussed in \citet{li2024automated}, the lineup protocol
has significant limitations in large-scale applications due to
dependence on human labor. Thus, a computer vision model was developed
with an associated statistical testing procedure to automate the
assessment of residual plots. This model takes a residual plot and a
vector of auxiliary variables (such as the number of observations) as
inputs and outputs the predicted visual signal strength (VSS). This
strength estimates the distance between the residual distribution of the
fitted regression model and the reference distribution assumed under
correct model specification.

To make the statistical testing procedure and trained computer vision
model widely accessible, we developed the R package \texttt{autovi}, and
a web interface, \texttt{autovi.web} to make it easy for users to
automatically read their residual plots with the trained computer vision
model.

>>>>

As noted in \citet{li2024automated}, the lineup protocol has significant
limitations in large-scale applications due to its reliance on human
labor. To overcome this constraint, a computer vision model was
developed alongside a corresponding statistical testing procedure to
autmoate the assessment of residual plots. The model takes as input a
residual plot and a set of auxiliary variables (such as the number of
observations) and outputs a predicted visual signal strength (VSS). This
VSS estimates the degree of deviation between the residual distribution
of the fitted model and the reference distribution expected under
correct model specification.

To make the statistical testing procedure and trained computer vision
model widely accessible, we developed the R package \texttt{autovi}
along with a companion web interface, \texttt{autovi.web}, which allows
users to automatically assess their residual plots using the trained
computer vision model.
